---
title: "IATweight"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(data.table)
library(ggplot2)
library(haven)
library(psych)
library(DataExplorer)
```

Loading in the project implicit datasets
```{r}
IAT04 <- read_sav("~/Implicit_datasets/Weight IAT.public.2004.sav")
IAT05 <- read_sav("~/Implicit_datasets/Weight IAT.public.2005.sav")
IAT06 <- read_sav("~/Implicit_datasets/Weight IAT.public.2006.sav")
IAT07 <- read_sav("~/Implicit_datasets/Weight IAT.public.2007.sav")
IAT08 <- read_sav("~/Implicit_datasets/Weight IAT.public.2008.sav")
IAT09 <- read_sav("~/Implicit_datasets/Weight IAT.public.2009.sav")
IAT10 <- read_sav("~/Implicit_datasets/Weight IAT.public.2010.revised.sav")
IAT11 <- read_sav("~/Implicit_datasets/Weight IAT.public.2011.revised332017.sav")
IAT12 <- read_sav("~/Implicit_datasets/Weight IAT.public.2012.revised.sav")
IAT13 <- read_sav("~/Implicit_datasets/Weight IAT.public.2013.revised.sav")
IAT14 <- read_sav("~/Implicit_datasets/Weight IAT.public.2014.revised.sav")
IAT15 <- read_sav("~/Implicit_datasets/Weight IAT.public.2015.sav")
IAT16 <- read_sav("~/Implicit_datasets/Weight IAT.public.2016.sav")
IAT17 <- read_sav("~/Implicit_datasets/Weight IAT.public.2017.sav")
IAT18 <- read_sav("~/Implicit_datasets/Weight_IAT.public.2018.sav")
IAT19 <- read_sav("~/Implicit_datasets/Weight IAT.public.2019.sav")
IAT20 <- read_sav("~/Implicit_datasets/Weight_IAT.public.2020.sav")
```

Subsetting the variables of interest. In this case, we are interested in attitude measures as well as gender. I also include a measure of geography in case there are any future regional analyses we wish to follow up on.
```{r}
Weight_att_2004 <- select(IAT04, D_biep.Thin_Good_all,att_5, tfat, tthin, sex, STATE)

Weight_att_2005 <- select(IAT05, D_biep.Thin_Good_all,att_5, tfat,tthin, sex, STATE)

Weight_att_2006 <- select(IAT06, D_biep.Thin_Good_all,att_5,att_7, tfat,tthin, sex, STATE)

Weight_att_2007 <- select(IAT07, D_biep.Thin_Good_all,att_7, tfat,tthin, sex, STATE)

Weight_att_2008 <- select(IAT08, D_biep.Thin_Good_all,att_7,tfat,tthin, sex, STATE)

Weight_att_2009 <- select(IAT09, D_biep.Thin_Good_all,att_7,tfat,tthin, sex, STATE)

Weight_att_2010 <- select(IAT10,D_biep.Thin_Good_all,att_7,att_reversed,tfat,tfat_1to11_reversed,tthin,tthin_1to11_reversed, dem_sex, sex, STATE) #45488 is the end of att_7 45488

Weight_att_2011 <- select(IAT11, D_biep.Thin_Good_all, att_reversed, tfat_1to11_reversed, tthin_1to11_reversed, dem_sex, STATE)

Weight_att_2012 <- select(IAT12, D_biep.Thin_Good_all, att_reversed, tfat_1to11_reversed, tthin_1to11_reversed, dem_sex, STATE)

Weight_att_2013 <- select(IAT13, D_biep.Thin_Good_all, att_reversed, tfat_1to11_reversed, tthin_1to11_reversed, dem_sex, STATE)

Weight_att_2014 <- select(IAT14, D_biep.Thin_Good_all, att_reversed, tfat_1to11_reversed, tthin_1to11_reversed, dem_sex, STATE)

Weight_att_2015 <- select(IAT15, D_biep.Thin_Good_all, weightpref_001, tempfat_001, tempthin_001, sex, STATE)

Weight_att_2016 <- select(IAT16, D_biep.Thin_Good_all,weightpref_001,att7, tfat,tempfat_001, tthin,tempthin_001, sex, birthsex, STATE)

Weight_att_2017 <- select(IAT17, D_biep.Thin_Good_all, att7, tfat, tthin, birthsex, STATE)

Weight_att_2018 <- select(IAT18, D_biep.Thin_Good_all, att7, tfat, tthin, birthSex, STATE)

Weight_att_2019 <- select(IAT19, D_biep.Thin_Good_all, att7, tfat, tthin, birthSex, STATE)
Weight_att_2020 <- select(IAT20, D_biep.Thin_Good_all, att7, tfat, tthin, birthSex, STATE)
```
For the attitude scales, a low number is a preference for fat over thin people.
For the thermometers, a low number reflects cold feelings towards the group.
The weightpref variable is measured the same as att7_reversed variable.


Now, I will begin to group datasets together that included constructs that were measured in similar ways (e.g., grouping datasets in which attitudes were measured with a 5-point scale vs. 7-point scale).

I am grouping datasets together that used a 5-point attitude scale and then standardizing their scores (2004-2006)
```{r}
Weight04_06 <- rbind(Weight_att_2004, Weight_att_2005, Weight_att_2006[c(1:152311),c(1:2,4:7)])
Weight04_06$att_5 <- scale(Weight04_06$att_5)
```

I am recoding the gender variable and then reverse scoring different attitude measures.
```{r}
#changing names of reverse scored variables
colnames(Weight_att_2015)[2] <- "att_reversed"
colnames(Weight_att_2015)[3] <- "tfat_1to11_reversed"
colnames(Weight_att_2015)[4] <- "tthin_1to11_reversed"
colnames(Weight_att_2016)[2] <- "att_reversed"
colnames(Weight_att_2016)[5] <- "tfat_1to11_reversed"
colnames(Weight_att_2016)[7] <- "tthin_1to11_reversed"

#recoding the gender variable
Weight_att_2015 <- Weight_att_2015 %>% 
  mutate(dem_sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))

Weight_att_2016 <- Weight_att_2016 %>% 
  mutate(dem_sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))


Weight10_16a <- rbind(Weight_att_2010[c(45495:192,718), c(1,3,5,7,8,10)], Weight_att_2011, Weight_att_2012, Weight_att_2013, Weight_att_2014,Weight_att_2015[,c(1,2,3,4,7,6)],Weight_att_2016[c(1:51647),c(1,2,5,7,11,10)])


Weight10_16a <- Weight10_16a %>% 
  mutate(att7= 8-att_reversed,
         tfat = 12-tfat_1to11_reversed,
         tthin = 12-tthin_1to11_reversed)

Weight10_16b <- select(Weight10_16a, D_biep.Thin_Good_all, att7, tfat, tthin, dem_sex, STATE)
colnames(Weight10_16)[2] <- "att_7"
```


I am merging the dataframes together that use 7point attitude scales and standardizing
```{r}
aList <- list("Weight10_16b","Weight_att_2017","Weight_att_2018","Weight_att_2019","Weight_att_2020")

for(i in aList){
  aux <- get(i)
  names(aux)[2] <- c("att_7")
  assign(i,aux)
}

aList2 <- list("Weight_att_2017", "Weight_att_2018", "Weight_att_2019", "Weight_att_2020", "Weight10_16b")

for(i in aList2){
  aux <- get(i)
  names(aux)[5] <- c("sex")
  assign(i,aux)
}

colnames(Weight_att_2016)[3] <- "att_7"
colnames(Weight_att_2016)[9] <- "sex"


Weight_att_2006 <- Weight_att_2006 %>% 
  mutate(sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))
Weight_att_2007 <- Weight_att_2007 %>% 
  mutate(sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))
Weight_att_2008 <- Weight_att_2008 %>% 
  mutate(sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))
Weight_att_2009 <- Weight_att_2009 %>% 
  mutate(sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))
Weight_att_2010 <- Weight_att_2010 %>% 
  mutate(sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))
Weight_att_2016 <- Weight_att_2016 %>% 
  mutate(sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))


Weight06_20 <- rbind(Weight_att_2006[c(152313:164,986),c(1,3:7)], Weight_att_2007,Weight_att_2008, Weight_att_2009, Weight_att_2010[c(1:45488),c(1,2,4,6,9,10)], Weight10_16b, Weight_att_2016[c(51650:258,734),c(1,3,4,6,9,10)], Weight_att_2017,Weight_att_2018, Weight_att_2019, Weight_att_2020)

Weight06_20$att_7 <- scale(Weight06_20$att_7)
```

I am binding the two dataframes together and creating temperature thermometer difference score.
```{r}
aList3 <- list("Weight04_06", "Weight06_20")

for(i in aList3){
  aux <- get(i)
  names(aux)[2] <- c("att")
  assign(i,aux)
}

Weight04_06 <- Weight04_06 %>% 
  mutate(sex = ifelse(sex == "f", 1, ifelse(sex == "m", 2, NA)))

allYears <- rbind(Weight04_06,Weight06_20)

allYears$therm.diff <- allYears$tthin - allYears$tfat

colnames(allYears)[1] <- "Dscore"
```

Running some data checks and making sure that the range of possible values make sense.
```{r}
plot_histogram(allYears)
plot_bar(allYears)
```

Saving this cleaned dataset to a new csv file
```{r}
write.csv(allYears, "cleaned_IAT_data.csv")

#I'm saving a smaller subset of the data that I can upload to github in order to give others an idea of what my final dataset looks like. 
allYears_subset <- allYears[1:500,]
write.csv(allYears_subset, "cleaned_IAT_data_subset.csv")
```


